Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-15 index.Rmd
clean yaml

---
title: "Global study of well-being and internet adoption | Online analysis supplement"
description: |
  Online analysis supplement for "A global study of adolescents’ digital technology adoption and its associations with well-being and mental health" (Vuorre and Przybylski, in prep)
author: "<a href='https://vuorre.netlify.app'>Matti Vuorre</a> & Andy Przybylski"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::bs4_book
url: https://digital-wellbeing.github.io/global-wbmh
biblio-style: apalike
---

>>>>

---
title: Global study of well-being and internet adoption | Online analysis supplement
description: |
  Online analysis supplement for "A global study of adolescents’ digital technology adoption and its associations with well-being and mental health" (Vuorre and Przybylski, in prep)
author: Matti Vuorre & Andy Przybylski
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::bs4_book
url: https://digital-wellbeing.github.io/global-wbmh
biblio-style: apalike
---

# Preface
